% LaTeX engine: XeLaTeX
\documentclass{resume}

\begin{document}

\header{Engineer in Computer Science\\and Artificial Intelligence}

\sidepanel{
	\contact{Contact}{
		\iconentry{location}{Address}{63 Chemin du Moulin, 38660, La Terrasse, FRANCE}

		\bigjump
		\iconentry{phone}{Phone Number}{\link{tel:+33751648450}{+33 7 51 64 84 50}}

		\bigjump
		\iconentry{email}{Email}{\link{mailto:Valentin.berger38@gmail.com}{Valentin.berger38@gmail.com}}

		\bigjump
		\iconentry{linkedin}{LinkedIn}{\link{https://www.linkedin.com/in/valentinberger/}{linkedin.com/in/valentinberger}}

		\bigjump
		\iconentry{skype}{Skype}{valentin.berger}

		\bigjump
		\iconentry{github}{GitHub}{\link{https://github.com/Cynnexis}{https://github.com/Cynnexis}}
	}

	\languages{Languages}{
		\iconentry{flag-fr}{French}{Native language}

		\bigjump
		\iconentry{flag-ca}{English}{Fluent, C1 Level (CEFR),\\TOEIC 955/990}

		\bigjump
		\iconentry{flag-es}{Spanish}{Basic command}
	}

	\interests{Interests}{
		\firstwindowicon{running}{\entrydescription{Running}}

		\jump
		\firstwindowicon{write}{\entrydescription{Writing}}

		\jump
		\firstwindowicon{computer}{\entrydescription{Computing}}

		\jump
		\firstwindowicon{space}{\entrydescription{Space}}
	}
	\vfill
}%
\hfill
\mainpanel{
	\displomas{Diplomas}{
		\entrytitle{Master's Degree in Artificial Intelligence}
		\entrydate{2019 -- Today}
		\entrydescription{Université Lyon 1, double degree with Computer Engineering curriculum}
		
		\jump
		\entrytitle{Computer Science \& Engineering Student at Polytech (Lyon, France)}
		\entrydate{2017 -- Today}
		\entrydescription{Polytech Lyon, 5\textsuperscript{th} year of study}

		\jump
		\entrytitle{First and second year of a Bachelor's Degree in Computer Science and\\Mathematics}
		\entrydate{2015 -- 2017}
		\entrydescription{Université Grenoble Alpes, two years of preparatory class for Polytech}
	}

	\work{Professional Experiences}{
		\entrytitle{Solutec Lyon}
		\entrydescription{Digital service company specialized in consulting}
		\entrydate{March 2020 to July 2020 -- 5 months}
		\entrydescription{
			Research \& Development internship. The mission was to build a Chatbot for the Solutec employees to answers their questions about the organization.

			\begin{itemize}
				\item Natural language processing using spaCy,
				\item Created neural network with TensorFlow framework.
			\end{itemize}
		}

		\jump
		\entrytitle{McMaster University \& TOTAL}
		\entrydescription{McMaster is a university located in Hamilton, Canada. TOTAL is a French petroleum company.}
		\entrydate{September 2018 to January 2019 -- 5 months}
		\entrydescription{
			Research internship in Mathematical Optimization.
			The goal was to handle the formulation of a mathematical model on an oil refinery in order to manage the uncertainty of shutting down machines for different durations.

			\begin{itemize}
				\item Wrote a multiperiod model,
				\item Understand how mathematical optimizers work,
				\item Contributed to a scientific journal,
				\item Implemented a GUI in HTML, CSS, PHP and JavaScript.
			\end{itemize}
		}

		\jump
		\entrytitle{STMicroelectronics Crolles}
		\entrydescription{A manufacturer of semiconductors}
		\entrydate{July and August 2017 -- 2 months}
		\entrydescription{
			Temporary job as operator in clean-room

			\begin{itemize}
				\item Maintained machines in the Lithography area.
			\end{itemize}
		}
		\entrydate{June 2016 -- 1 month}
		\entrydescription{
			Internship at a company as a developer assistant

			\begin{itemize}
				\item Used a statistical model to control products quality on the assembly line,
				\item Designed an application in C\# using .NET framework.
			\end{itemize}
		}
	}

	\skills{Skills}{
		\entrytitle{Programming Languages, Scripts and Frameworks}
		\entrydescription{
			\begin{itemize}
				\item C, C++, C\#, Java, Kotlin, Python and LaTeX
				\item HTML5, CCS3, JavaScript, PHP, OracleSQL, R, Matlab and GAMS
				\item Good command of Android Native and TensorFlow
				\item Basic command of Qt (C++ Framework), VueJS and Flutter
			\end{itemize}
		}
	}

	%\cvfootnote{This document has been compiled with {\DejaSans ❤️} by {\fontfamily{lmr}\selectfont\LaTeX{}}}
}

\end{document}
